On exponential sums arising from the classical doubling method

### 2025-04-08 main.tex
Correction

The main result of this paper is 
\begin{theorem}
\label{thm:Phi_stable}
	The assignments $H \to \cComplex$ given by $$h \mapsto \genHermitianJacobiKernel{\hermitianSpace}{h}$$ are stable functions. Equivalently, the assignments $$\pi \mapsto \dblJacobiSumScalar{\pi}{\chi}$$ are constant on geometric Lusztig series.
\end{theorem}
%In the $\GL_n$ case, \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo}

>>>>

The main result of this paper is 
\begin{theorem}
\label{thm:Phi_stable}
	The assignments $H \to \cComplex$ given by $$h \mapsto \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(h\right)$$ are stable functions. Equivalently, the assignments $$\pi \mapsto \dblJacobiSumScalar{\pi}{\chi}$$ are constant on geometric Lusztig series.
\end{theorem}
%In the $\GL_n$ case, \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo}
